%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4j]{jarticle}

\usepackage{comment}
\usepackage{jsaisig}
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipdfmx]{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\todo[1]{@TODO[#1]}


\begin{document}
% 和文タイトル
\title{RoboCup Rescue Virtual Robot Leagueを使った教材開発の検討}

% 英文タイトル
\etitle{A Proposal of a robotic educational material with RoboCup Rescue Virtual Robot League Environment} 

% 著者名: 
%	・各著者を\quad（全角空白）区切りで列挙
% 	・著者名の直後に\afil{所属番号}を追加→所属番号を上付で出力（\textsuperscript{所属番号}と同じ）
% 	　複数機関へ所属している場合は番号をカンマ区切りで列挙（下記著者２参照）
% 　・Corresponding Authorについては所属の後に\thanksを続け，連絡先を記入
%	・英文著者はカンマ区切りで列挙
\author{西村　秀樹\afil{1}%
 	\thanks{%
    連絡先： 名城大学 理工学部 情報工学科 \newline%
    〒468-8502 名古屋市天白区塩釜口1-501 \newline%
  	 E-mail: {133430011@ccalumni.meijo-u.ac.jp}%
  }%
 	\quad 清水 優\afil{2} \quad 高橋 友一\afil{1}\\
  Hideki Nishimura\afil{1} \quad Masaru Shimizu\afil{1} \quad Tomoichi Takahashi\afil{1}
}

% 所属
\affiliation{%
 	\afil{1} 名城大学 理工学部 情報工学科\\
 	\afil{2} 中京大学 工学部 機械システム工学科\\
  \afil{1} Meijo University, Department of Information Engineering\\
  \afil{2} Chukyo University, School of Engineering
}

\abstract{%
RoboCup world champion ship has the Rescue Virtual Robot League(RVRL). The simulation environment of RVRL consists of USARSim and WSS, ROS. USARSim is a realistic physical simulator with several rescue robot models and victims, sensors, obstacles, convenience parts for making disaster field model. WSS is Wireless Simulation Server to realize the controllable wireless environment. For example, depending on the distance of robots, WSS can connect and disconnect wireless communication between a couple of robots. ROS is a kind of Robot Operating System Library. It makes easy to write some nice robotic softwares. Those RVRL simulation environment is good at an education scene in robotics. The realistic simulator's representation increase will not only keep but also increase student's motivation. WSS will change the simulated disaster field into challenging and wondering one. Students will be able to make robotic programs more fast and easy than before.
Those are reasons to propose making an educational simulation environment with the RVRL simulation environment.
}

\maketitle
\thispagestyle{empty}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{はじめに}\label{sec:introduction}
とりあえずアブストラクトの日本語訳でいいんじゃない．

\section{これまでの開発環境の問題点}\label{sec:related-works}
これまでの開発環境の問題点としては，
リアルじゃない
仮想環境の再構築が難しい
同時に使用できるロボットの種類が少ない
実際のレスキューロボットのモデルでは無い
災害現場の状況が再現できてない
ロボットのプログラムを構築するのが難しい＝初心者向きでは無い
上記問題点を解決できない
という問題がある

\section{提案する学習用ロボット環境のメリット}\label{sec:the-merit-of-our-proposal}
USARSimを，使用することでリアルなシミュレーション画像が得られる
USARSimは，レスキューロボット用に調整されており，実際のレスキューロボットのモデルが多数用意されている
USARSimは，
サーバークライアントモデルなので，１つのシミュレーション環境中で複数のロボットを参加させることができ，現実世界中での競争のようなことも実現できる

\subsection{USARSim}
\subsection{WSS}
\subsection{ROS}

\section{まとめ}
十分にリアルでかつ実際の災害現場を模した学習用ロボット仮想環境の提案をした.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{謝辞}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{99}
%\small

\bibitem{abbas:13}
{{Abbas, A.}, {Muhammad, S.}}:
{Homophily, Popularity and Randomness: Modelling Growth of Online Social Network}
{\it AAMAS 2013} (2013)

\bibitem{fridman:13}
{{Fridman, N.}, {Kaminka, G.}, {Zilka, A.}}:
{The Impact of Culture on Crowd Dynamics: An Empirical Approach}
{\it AAMAS 2013} (2013)
\bibitem{:13}

{{Hui, C.}, {Goldberg, M.}, {Magdon-Ismail, M.}, {Wallace, W.}}:
{Simulating the Diffusion of Information: An Agent-Based Modeling Approach}
{\it AAMAS 2013} (2013)

\bibitem{muramoto:2012}
邑本 俊亮:
避難と情報
{\it 電子情報通信学会誌}, Vol.~95, No.~10, pp.~894--898 (2012)

\bibitem{tokuda:2011}
徳田 雄洋:
震災と情報?あのとき何が伝わったか
{\it 岩波書店}, (2011)

\bibitem{COMMUNICATIONS}
{Walle, B.}, {Turoff, B.}:
{Emergency Response Information Systems: EMERGING TRENDS AND TECHNOLOGIES}
{\it Association for Computing Machinery}, Vol.~50, No.~3, pp.~29--31 (2007)

\bibitem{Nuria07}
Nuria Pelechano and Ali Malkawi:
Comparison of crowd simulaton for building evacuation and an alternateive approach
{\it In Building Simulation 2007}, pp.~1514--1514 (2007)

\bibitem{aamas11jason}
Jason Tsai et al.:
{{ESCAPES} - Evacuation Simulation with Children, Authorities, Parents, Emotions, and Social comparison}
{\it AAMAS 2011}, (2011)

\bibitem{okaya:2010}
岡谷賢, 高橋友一:
人間関係を考慮したエージェントベースの避難シミュレーションフ レームワーク
{\it 電子情報通信学会誌}, Vol.~J94, No.~11, pp.~1855--1865 (2011)

\bibitem{drabek}
Drabek, T.:
The Human Side of Disaster, Second Edition
{\it CRS Press}, Vol.~95, No.~10 pp.~859--952 (2013)

\bibitem{stanford-sns}
Stanford University:
Social circles: Facebook
{http://snap.stanford.edu/data/egonets-Facebook.html}

\bibitem{NIST}
Averill, J.:
NISTncstar 1-7: Occupant behavior, egress, and emergency communication
(2005)

\bibitem{shanon}
クロード・E. シャノン, ワレン ウィーバー:
通信の数学的理論
{\it 筑摩書房} (2009)


\begin{comment}
\bibitem{}
First, A., Second, A.:
Homophily, Popularity and Randomness: Modelling Growth of Online Social Network
{\it Journal Name}, Vol.~xx, No.~x, pp.~xx--xx (2007)
\end{comment}




\end{thebibliography}

\end{document}